Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex
added some references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Diffusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in porous media is often characterized in terms of
anomalous diffusion~\cite{} \todo[inline]{need references}, and the
anomalous diffusion rate depends on the properties of the geometry.  The
anomalous diffusion depends on the porosity~\cite{}, but the
distribution of the bodies also affects the anomalous diffusion rates.
Since erosion causes certain structure in porous media, calculating the
anomalous diffusion rates in these geometries is important.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Diffusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in porous media is often characterized in terms of
anomalous diffusion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}, and the
anomalous diffusion rate depends on the properties of the geometry.  The
anomalous diffusion depends on the porosity and
permeability~\cite{koc-bra1988}, but the distribution of the bodies also
affects the anomalous diffusion rates.  Since erosion causes certain
structure in porous media, calculating the anomalous diffusion rates in
these geometries is important.
